Containers and R---the Rockerverse and beyond

### 2019-12-07 manuscript.Rmd
allow the manuscript to build with the CRAN version of rticles

```{r setup, include=FALSE}
library(tidyverse)
library(kableExtra)
```

@@

```{r clientfunctionalities, echo=FALSE, results='asis', warning=FALSE, message=FALSE,}

library(kableExtra)

functionalities <- tribble(
  ~id, ~Functionality,
  "dockerfile", "Generate a Dockerfile",
  "build", "Build an image",
  "execute", "Execute a container locally or remotely",
  "cloud", "Deploy or manage an instances in the cloud",
  "interact", "Interact with an instance (e.g. file transfer)",
  "images", "Manage storage of images",
  "othercontainers", "Supports Docker and Singularity",
  "api", "Direct access to Docker API instead of using the CLI",
  "install", "Installing Docker software"
)

@@

knitr::kable(tab, escape = FALSE) %>% 
  # kable_styling(latex_options = "striped") %>%
  row_spec(0, angle = -90)
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
```

@@

```{r clientfunctionalities, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
functionalities <- tribble(
  ~id, ~Functionality,
  "dockerfile", "Generate a Dockerfile",
  "build", "Build an image",
  "execute", "Execute a container locally or remotely",
  "cloud", "Deploy or manage an instances in the cloud",
  "interact", "Interact with an instance (e.g. file transfer)",
  "images", "Manage storage of images",
  "othercontainers", "Supports Docker and Singularity",
  "api", "Direct access to Docker API instead of using the CLI",
  "install", "Installing Docker software"
)

@@

# inserting a table in the R Journal currently fails
# waiting for this PR to merge
# https://github.com/rstudio/rticles/pull/261
if (packageVersion("rticles") >= "0.12.3") {
  requireNamespace("kableExtra")
  knitr::kable(tab, escape = FALSE) %>%
    kableExtra::row_spec(0, angle = -90)
} else {
  cat("\n\n[Functionality overview table omitted due to a small bug in rticles]\n\n")
}
```
